Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-02-10 manuscript/cpcrw_manuscript.Rmd
Gravimetric WC update
Data corrections due to sorting and data entry mistakes. See issue #38.
Added Tukey HSD test on cumulative fluxes

```{r, echo=FALSE, results='hide', message=FALSE, fig.keep='none'}
library(dplyr, warn.conflicts = FALSE)
setwd("../")
source("R/5-analyze.R")
```

@@

The incubation experiment concluded on 9 December 2015, following the final CO~2~ and CH~4~ readings. Each soil core was maintained at the treatment-dependent temperature and moisture content (by mass) until removed for destructive sampling, December 14-18, 2015. Sub-samples were collected and composited throughout each soil core for dissolved organic carbon analysis (110 ± 24 g dry mass equivalent) and dry-mass calculations (~28 g each). The remaining core material was air-dried and separated into particles (>2 mm diameter) and soil (<2 mm) using a U.S. Standard Test Sieve No. 10 (Fisherbrand,  Pittsburg, PA, USA). The dry mass and volume of soil were used in calculations of gravimetric and volumetric soil moisture content, respectively {Gardner, 1986 #4345}. Soil volume was caclulated as the total core volume minus the volume of particles >2 mm diameter, with the latter determined by water displacement. Air-dried soil and sub-samples stored at -20 °C were sent to the Agricultural and Environmental Services Laboratory at the University of Georgia Extension in February 2016 for total C, N, and dissolved organic C. TODO: get UGA analytical methods.

@@

We measured the rise in GHG concentrations from its minimum value (in the first 10 seconds of measurement after the analyzer was sealed to the soil core) to its maximum (in the first 45 seconds), considering this as the flux rate in ppm s^-1^ (CO2) or ppb s^-1^ (CH4). This value was calculated for each sample, i.e. each individual core measurement throughout the 100-day incubation.

@@

@@

* Cumulative fluxes (Figure 4)
* CO2:CH4 ratios
* Statistical tests of WC and temperature on cumulative fluxes

>>>>

```{r, echo=FALSE, results='hide', message=FALSE, fig.keep='none'}
pclean <- function(x) {  # pretty formatting of p-values
  ifelse(x < 0.001, "< 0.001", paste("=", formatC(x, digits = 3, format = 'f'))) %>%
    paste("P", .)
}

library(dplyr, warn.conflicts = FALSE)
setwd("../")
source("R/5-analyze.R")
```

@@

The incubation experiment concluded on 9 December 2015, following the final CO~2~ and CH~4~ readings. Each soil core was maintained at the treatment-dependent temperature and moisture content (by mass) until removed for destructive sampling, December 14-18, 2015. Sub-samples were collected and composited throughout each soil core for dissolved organic carbon analysis (110 ± 24 g dry mass equivalent) and dry-mass calculations (~28 g each). The remaining core material was air-dried and separated into particles (>2 mm diameter) and soil (≤2 mm) using a U.S. Standard Test Sieve No. 10 (Fisherbrand,  Pittsburg, PA, USA). The dry mass and volume of soil were used in calculations of gravimetric and volumetric soil moisture content, respectively {Gardner, 1986 #4345}. Soil volume was caclulated as the total core volume minus the volume of particles >2 mm diameter, with the latter determined by water displacement. Air-dried soil and sub-samples stored at -20 °C were sent to the Agricultural and Environmental Services Laboratory at the University of Georgia Extension in February 2016 for total C, N, and dissolved organic C. TODO: get UGA analytical methods.

@@

We measured the rise in GHG concentrations from its minimum value (in the first 10 seconds of measurement after the analyzer was sealed to the soil core) to its maximum (in the first 45 seconds), considering this as the flux rate in ppm s^-1^ (CO~2~) or ppb s^-1^ (CH~4~). This value was calculated for each sample, i.e. each individual core measurement throughout the 100-day incubation.

@@

The effect of temperature and treatment (drought, controlled drought, or field moisture conditions) on cumulative gas fluxes was evaluted with a post-hoc Tukey Honest Significant Differences test.

@@

* Cumulative fluxes (Figure 4)

Cumulative CO~2~ evolved was highly affected by temperature (`r pclean(co2_hsd$Temperature["p adj"])`), and field moisture cores emitted significantly more CO~2~ than the other two treatments at both temperatures (P < 0.001 for both). There was no difference between the 20 °C drought and controlled drought treatments (`r pclean(co2_hsd$Treatment["Drought-Controlled drought", "p adj"])`). Neither temperature (`r pclean(ch4_hsd$Temperature[,"p adj"])`) nor treatment (mean `r pclean(mean(ch4_hsd$Treatment[,"p adj"]))`) was a significant factor in predicting cumulative CH~4~ fluxes.

* CO2:CH4 ratios
* Statistical tests of WC and temperature on cumulative fluxes
